The State of Graph Processing \\ \large APIs, Libraries, Benchmarks, and Programming Languages \vspace{-1em}

### 2017-01-13 papers/gabb17/gabb17-pollard.tex
Started GABB17 paper. Moved writeups to papers/
Next order of business is to get some reference impelementations
all going on ACISS or some standard platform.

\documentclass{sig-alternate}
%\documentclass[11pt]{article}
%\usepackage[margin=1in, headheight=15pt]{geometry} % No geometry with sig-alternate
%\usepackage{fancyhdr, setspace}
%\renewcommand{\headrulewidth}{0pt}
%\pagestyle{fancy}
%\setlength{\headheight}{15pt} % Removes warnings. Set to 30pt if 2 lines on the header.
%\lhead{}
%\rhead{}
%\usepackage{totcount}
%\regtotcounter{page}
%\cfoot{\ifnum\totvalue{page} > 1 \thepage \else\fi}
%\usepackage{amsmath, amsthm, amsfonts}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.12}
\usepackage{booktabs}

@@

\begin{document}
%%% ACM title stuff %%%
\setcopyright{acmcopyright}
\doi{?}
\isbn{?}
%\acmPrice{}
\conferenceinfo{Load Testing and Benchmarking of Software Systems (LTB)}{2017, L'Aquila, Italy}
\title{Simplifying Parallel Graph Processing}
\subtitle{A Survey of Existing Platforms}
\numberofauthors{2}
\author{
\alignauthor
	Samuel Pollard\\
	\affaddr{University of Oregon}\\
	\affaddr{Eugene, OR, USA}\\
	\email{spollard@cs.uoregon.edu}
\alignauthor
	Boyana Norris\\
	\affaddr{University of Oregon}\\
	\affaddr{Eugene, OR, USA}\\
	\email{norris@cs.uoregon.edu}
}
% Generated from http://dl.acm.org/ccs/ccs.cfm
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10011007.10010940.10011003.10011002</concept_id>
	<concept_desc>Software and its engineering~Software performance</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Software and its engineering~Software performance}

%%% Normal title stuff %%%
%\title{Simplifying Parallel Graph Processing: \\
%	\large Survey of Existing Platforms
%}
%\author{Samuel Pollard (\href{mailto:spollard@cs.uoregon.edu}{spollard@cs.uoregon.edu})}
%\date{\today}
\maketitle

\begin{abstract}
This is a survey of existing graph analytics frameworks.
\end{abstract}

@@

% TODO: Make this a pgfplotstable with an automatically generated csv.
\begin{table}[!htb]
	\centering
% Arya
%	\begin{tabular}{l|r}
%		CPU & 72 Core Intel Xeon E5 2699 v3\\ \hline
%		RAM & 256 GB DDR4 2133 MHz
%	\end{tabular}

% Keep in mind you can do this at the beginning: string replace={s1}{s2}
	\pgfplotstabletypeset[
	header=false,
	col sep=tab,
	string type,
    every head row/.style={output empty row, before row=\bottomrule},
	columns/0/.style={column type={|r|}},
	columns/1/.style={column type={l|}},
	every last row/.style={after row=\toprule},
	]{specs.csv}
	\caption{Machine specifications. The disparity between the CPU's advertised clock speed and the ``CPU Clock'' row is a result of the Turbo Boost technology which can increase the clock speed to a limit. The manufacturer's published maximum clock speeds can be found at \url{http://ark.intel.com}.}
	\label{tab:specs}
\end{table}

%\begin{table}[htb]
%	\centering
%	\begin{tabular}{lr}
%		Transport & \\ \hline
%		Network Topology & \\ \hline
%		Local Scheduling & \\ \hline
%		Runtime Feedback & \\ \hline
%		Approach & \\ \hline
%		Algorithmic Considerations & \\ \hline
%	\end{tabular}
%	\caption{Middleware specifications}
%	\label{tab:reportcard}
%\end{table}

@@

Table~\ref{tab:perf} lists performance in milliseconds of runtime according to the graphalytics output. Graphalytics also outputs MTEPS or millions of traversed edges pers econd. However, the graphalytics version does not make sense in all cases: for example, computing the local clustering coefficient involves traversing each edge multiple times (proportional to the sparsity of the graph), while breadth first search (BFS) traverses each edge exactly once, and on na\:ive implementations single-source shortest paths (SSSP) may have $O(|E| + |V|^2)$ traversed edges.
% TODO: Cite Comer algorithm book for Dijkstra's algorithm runtime.

@@

		\centering
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={[index]0,openg,powergraph},
			every head row/.style={after row=\midrule},
			columns/0/.style={string type, column type={l|}, column name={}},
			columns/openg/.style={string type, column type={r}},
			columns/powergraph/.style={string type, column type={r}}
		]{runtime.csv}
	\caption{Performance Results for the \texttt{dota-league} dataset with 61,670 vertices and 50,870,313 edges.}
	\label{tab:perf}
\end{table}

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{table*}[t]
	\begin{minipage}{\linewidth} % So the footnotes all get printed on the same page
		\centering
		%\small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={Name,Type,HPC,Parallelism,Target,FOSS,Source,Notes},
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
%			columns/Comm./.style={%
%				string type,
%				postproc cell content/.style={%
%					@cell content/.add={\footnotesize}
%				}
%			},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{platforms.csv}
		\caption{Tools used for graph processing}
		\label{tab:frameworks}
	\end{minipage}
\end{table*}

@@

%\bibliographystyle{acm}
\bibliographystyle{abbrv}
\bibliography{drp}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.12}
\usepackage{booktabs}

@@

\title{A Comparison of Parallel Graph Processing Platforms}
\author{
	\IEEEauthorblockN{Samuel Pollard}
	\IEEEauthorblockA{Department of Computer and Information Science \\
		University of Oregon \\
		Eugene, OR, USA \\
		Email: spollard@cs.uoregon.edu
	}
	\and
	\IEEEauthorblockN{Boyana Norris}
	\IEEEauthorblockA{Department of Computer and Information Science \\
	University of Oregon \\
	Eugene, OR, USA \\
	Email: norris@cs.uoregon.edu
	}
}

\begin{document}
\maketitle
\begin{abstract}
This is a survey of existing graph analytics frameworks.
\end{abstract}

@@

% TODO: Make this a pgfplotstable with an automatically generated csv.
\begin{table}[!htb]
	\centering
	% Keep in mind you can do this at the beginning: string replace={s1}{s2}
	\pgfplotstabletypeset[
	header=false,
	col sep=tab,
	string type,
    every head row/.style={output empty row, before row=\bottomrule},
	columns/0/.style={column type={|r|}},
	columns/1/.style={column type={l|}},
	every last row/.style={after row=\toprule},
	]{../report/specs.csv}
	\caption{Machine specifications. The disparity between the CPU's advertised clock speed and the ``CPU Clock'' row is a result of the Turbo Boost technology which can increase the clock speed to a limit. The manufacturer's published maximum clock speeds can be found at \url{http://ark.intel.com}.}
	\label{tab:specs}
\end{table}

\begin{table}[htb]
	\centering
	\begin{tabular}{l|c|c|c}
			& BFS & SSSP & PR \\ \hline
		Graph500 & & & \\ \hline
		PBGL  & & & \\ \hline
		GAP  & & & \\ \hline
		GraphBIG  & & & \\ \hline
		Galois  & & & \\ \hline
		PowerGraph  & & &
	\end{tabular}
	\caption{Performance. Note that implementations of every algorithm are not availabe for every platform.}
	\label{tab:reportcard}
\end{table}

@@

%Table~\ref{tab:perf} lists performance in milliseconds of runtime according to the graphalytics output. Graphalytics also outputs MTEPS or millions of traversed edges pers econd. However, the graphalytics version does not make sense in all cases: for example, computing the local clustering coefficient involves traversing each edge multiple times (proportional to the sparsity of the graph), while breadth first search (BFS) traverses each edge exactly once, and on na\:ive implementations single-source shortest paths (SSSP) may have $O(|E| + |V|^2)$ traversed edges.
% TODO: Cite Comer algorithm book for Dijkstra's algorithm runtime.

@@

		\centering
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={[index]0,openg,powergraph},
			every head row/.style={after row=\midrule},
			columns/0/.style={string type, column type={l|}, column name={}},
			columns/openg/.style={string type, column type={r}},
			columns/powergraph/.style={string type, column type={r}}
		]{../report/runtime.csv}
	\caption{Performance Results for the \texttt{dota-league} dataset with 61,670 vertices and 50,870,313 edges.}
	\label{tab:perf}
\end{table}

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{table*}[t]
	\begin{minipage}{\linewidth} % So the footnotes all get printed on the same page
		\centering
		%\small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={Name,Type,HPC,Parallelism,Target,FOSS,Source,Notes},
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
%			columns/Comm./.style={%
%				string type,
%				postproc cell content/.style={%
%					@cell content/.add={\footnotesize}
%				}
%			},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{../report/platforms.csv}
		\caption{Tools used for graph processing}
		\label{tab:frameworks}
	\end{minipage}
\end{table*}

@@

%\bibliographystyle{acm}
\bibliographystyle{IEEEtran}
\bibliography{../drp}
\end{document}

### 2017-01-13 papers/taxonomy/taxonomy.tex
Started GABB17 paper. Moved writeups to papers/
Next order of business is to get some reference impelementations
all going on ACISS or some standard platform.

	\item \textbf{GraphStream.} Java library; I'm not sure but it appears to be serial; \url{http://graphstream-project.org/}; \cite{Dutot:2007:GraphStream} first active 2007; appears still active.

@@

	\item \textbf{PGX.} Oracle Project. Supports incremental updates though the dynamic aspect is not forefront.
	% \item \textbf{DynoGraph.} Performance Analysis; \url{https://github.com/sirpoovey/DynoGraph} \cite{Hein:2016:DynoGraph}; connected components, PageRank, BFS; right now just a repo and a poster at SC'16.
\end{itemize}

@@

\bibliographystyle{plain}
\bibliography{../report/drp}

>>>>

	\item \textbf{GraphStream.} Java library; appears to be serial and focuses mainly on visualization; \url{http://graphstream-project.org/}; \cite{Dutot:2007:GraphStream} first active 2007 but appears active as of December 2016.

@@

	\item \textbf{PGX.} Oracle Project; integration with Groovy, Green Marl, Spark, Hadoop; Supports incremental updates though the dynamic aspect is listed as future work. \cite{Hong:2015:PGX}.
	% \item \textbf{DynoGraph.} Performance Analysis; \url{https://github.com/sirpoovey/DynoGraph} \cite{Hein:2016:DynoGraph}; connected components, PageRank, BFS; right now just a repo and a poster at SC'16.
\end{itemize}

@@

\bibliographystyle{plain}
\bibliography{../drp}
